`r params$doc_title`

### 2022-11-16 scripts/MSc.Rmd
added comments from last meeting

@@

- First analysis

@@

>>>>

-   2022-11-15: 
    1. Check if formula PVE numeric can be used for binary traits as well. Can the $\%var(X)$ – numeric – be compared with $\%var(U)$ $\%var(Y)$ – binary?
    2. How is $\%var$ calculated in the MRbase package in the `mr_steiger` function (Steiger filtering)?
    3. Prefer new formula for $\%var(X)$ calculation
    4. FTO gene: Add SNP associated with FTO gene to analysis that was considered ambiguous. Check the beta estimate from UK Biobank (provide rsID to Felix: `rs1558902`)
    5. Try also $K_{GBC}= 0.05/100$ for $\%var(Y)$ (before used $ASR=1.2/100.000$)
    6. Update „Figure 1“ to 6 parts
    7. Also run BMI -> GSD, FTO -> GSD + BMI -> GBC, FTO->GBC: How different are the MR methods in estimating the causal estimate?
    8. Reference estimates for simulation: Wald estimate (FTO variant) + IVW total sample + conmix total sample
    9. Plot PVE from all simulated variants as boxplots on each dot of Figure 01

@@

- Issues from discussion mentioned above

@@

### %var(X) BMI formula comparison

```{r}
ggplot(data=my_data_harm, aes(x=explained_variance_BMI, y=explained_variance_BMI2)) +
  geom_point(alpha=0.6)+
  geom_abline()+
  theme_few()
```
